\chapter{Publication List}

\section*{International Journals (peer reviewed)}

\begin{enumerate}
  \item \textbf{Tho Nguyen Duc}, Chanh Minh Tran, Nguyen Gia Bach, Phan Xuan Tan, Eiji Kamioka, ``Repetition-Based Approach for Task Adaptation in Imitation Learning'' Sensors, Vol. 22, Issue 18, 6959, 2022, pp.1-19.
  \item Nguyen Gia Bach, Chanh Minh Tran, \textbf{Tho Nguyen Duc}, Phan Xuan Tan, Eiji Kamioka, ``Novel projection schemes for graph-based Light Field coding'' Sensors, Vol. 22, Issue 13, 4948, 2022, pp.1-28.
  \item Chanh Minh Tran, \textbf{Tho Nguyen Duc}, Nguyen Gia Bach, Phan Xuan Tan, Eiji Kamioka, ``Sprinkle Prebuffer Strategy to Improve Quality of Experience with Less Data Wastage in Short-form Video Streaming'' Electronics, Vol. 11, Issue 13, 1949, 2022, pp.1-18.
  \item Chanh Tran Minh, \textbf{Tho Nguyen Duc}, Phan Xuan Tan, Eiji Kamioka, ``An Experimental Study of the Server-based Unfairness Solutions for the Cross-Protocol Scenario of Adaptive Streaming over HTTP/3 and HTTP/2'' Baghdad Science Journal (BSJ), Vol. 18, No. 4, 2021, pp.1441-1447.
  \item \textbf{Tho Nguyen Duc}, Chanh Minh Tran, Phan Xuan Tan, Eiji Kamioka, ``Generative Adversarial Network for Imitation Learning from Single Demonstration'' Baghdad Science Journal (BSJ), Vol. 18, No. 4, 2021, pp.1350-1355.
  \item Chanh Minh Tran, \textbf{Tho Nguyen Duc}, Phan Xuan Tan, Eiji Kamioka, ``Cross-protocol Unfairness between Adaptive Streaming Clients over HTTP/3 and HTTP/2: A Root-Cause Analysis'' Electronics, Vol. 10, Issue 15, 1755, 2021, pp.1-14.
  \item \textbf{Tho Nguyen Duc}, Chanh Minh Tran, Phan Xuan Tan, Eiji Kamioka, ``Domain Adaptation for Imitation Learning using Generative Adversarial Network'' Sensors, Vol. 21, Issue 14, 4718, 2021, pp.1-14.
  \item \textbf{Tho Nguyen Duc}, Chanh Minh Tran, Phan Xuan Tan, Eiji Kamioka, ``Convolutional Neural Networks for Continuous QoE Prediction in Video Streaming Services'' IEEE Access, Vol. 8, 2020, pp.116268-116278.
  \item Chanh Minh Tran, \textbf{Tho Nguyen Duc}, Phan Xuan Tan and Eiji Kamioka, ``FAURAS: A Proxy-based Framework for Ensuring the Fairness of Adaptive Video Streaming over HTTP/2 Server Push'' Applied Science, Vol. 10, Issue 7, 2485, 2020, pp.1-21.
  \item Chanh Minh Tran, \textbf{Tho Nguyen Duc}, Phan Xuan Tan, Eiji Kamioka, ``QABR: A QoE-Based Approach to Adaptive Bitrate Selection in Video Streaming Services'' International Journal of Advanced Trend in Computer Science and Engineering, Vol. 8, No. 1.4, 2019, pp.138-144.
  \item \textbf{Tho Nguyen Duc}, Chanh Minh Tran, Phan Xuan Tan, Eiji Kamioka, ``Modeling of Cumulative QoE in On-demand Video Services: Role of Memory Effect and Degree of Interest'' Future Internet, Vol.11, Issue 8, 171, 2019, pp.1-18.
\end{enumerate}

\section*{International Conferences (peer reviewed)}

\begin{enumerate}
  \item Chanh Minh Tran, \textbf{Tho Nguyen Duc}, Nguyen Gia Bach, Phan Xuan Tan, Eiji Kamioka, ``Reducing QoE Loss and Data Wastage of Short-Form Video Streaming with HTTP/3 Prioritization'' Proceedings of the 12th International Conference on Informatics, Environment, Energy and Applications 2023 (IEEA2023), Singapore, February 17-19, 2023 (Accepted).
  \item Long Doan, \textbf{Tho Nguyen Duc}, Chuanzhe Jing, Eiji Kamioka, Phan Xuan Tan, ``Automatic Keyword Extraction for Viewport Prediction of 360-degree Virtual Tourism Video'' Proceedings of the 2nd IEEE International Conference on Computing 2022 (ICOCO2022), Kota, Kinabalu, Sabah, Malaysia, November 14-16, 2022, pp.386-391.
  \item Chuanzhe Jing, \textbf{Tho Nguyen Duc}, Phan Xuan Tan, Eiji Kamioka, ``Subtitle-based Viewport Prediction for 360-degree Virtual Tourism Video, `` Proceedings of the 13th International Conference on Information, Intelligence, Systems and Applications 2022 (IISA2022), Corfu, Greece, July 18-20, 2022, pp.1-8.
  \item Phan Xuan Tan, \textbf{Tho Nguyen Duc}, Chanh Minh Tran, Eiji Kamioka, ``Continuous QoE Prediction Based on WaveNet'' Proceedings of the 12th International Conference on Computer and Automation Engineering (ICCAE2020), Sydney, Australia, February 14-16, 2020, pp.80-84.
  \item Yu Wang, Chanh Minh Tran, \textbf{Tho Nguyen Duc}, Xiaochun Wu, Phan Xuan Tan, Eiji Kamioka, ``An Experimental Study on the Unfairness in Adaptive Streaming with HTTP/2 Server Push'' Proceedings of International Conference on Video, Signal and Image Processing 2019 (VSIP2019), Wuhan, China, October 29-31, 2019, pp.94-98.
  \item \textbf{Tho Nguyen Duc}, Chanh Minh Tran, Phan Xuan Tan and Eiji Kamioka, ``Bidirectional LSTM for Continuously Predicting QoE in HTTP Adaptive Streaming'' Proceedings of the 2nd International Conference on Information Science and System (ICISS2019), Tokyo, Japan, March 16-19, 2019, pp.156-160.
\end{enumerate}

\section*{Domestic Conference (non-reviewed)}

\begin{enumerate}
  \item \textbf{Tho Nguyen Duc}, Chanh Minh Tran, Phan Xuan Tan, Eiji Kamioka, ``Imitation Learning: Learning Simple Tasks from a Single Demonstration using Generative Adversarial Network'' IEICE Technical Report, Vol.121, No.181, CNR2021-6, September 21, 2021, pp.12-15.
  \item Chanh Minh Tran, \textbf{Tho Nguyen Duc}, Phan Xuan Tan, Eiji Kamioka, ``Cross-Protocol Performance Investigation between HTTP/3 and HTTP/2: An Experiment with Adaptive Streaming'' IEICE Technical Report, Vol.121, No.167, IA2021-23, September 8, 2021, pp.54-58.
\end{enumerate}
